Automated Dynamic Slice Backsolving

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
various paper deets

Pintool, python specifics. Binarys, RE
how i implemented DTA

@@

TODO Even without reading system resources, there appears to be an issue of overtainting in Stubble's implementation.

@@

TODO learned about OS internals
TODO difficulties with implementation

>>>>

TODO
Pintool, python specifics. Binarys, RE
how i implemented DTA
Pin's API

@@

TODO better "vuln disc." conditions like segfaults, taint reaching EIP.

@@

TODO RE'd in IDA Pro a lot
TODO learned about OS internals
TODO difficulties with implementation
